### 2017-12-06 submission/manuscript.Rmd
add sequence processing methods section

>>>>

***Sequence Processing:***
The mothur software program was utilized for all sequence processing steps [@mothur_schloss_2009]. The protocol followed was similar to that used by Kozich, *et al.* [@protocol_Kozich_2013] (https://www.mothur.org/wiki/MiSeq_SOP). Two major differences from the stated protocol were the use VSEARCH instead of UCHIME for chimera detection and the use of the OptiClust algorithmn instead of average neighbor for OTU generation [@vsearch_Rognes_2016; @uchime_Edgar_2011; @opticlust_Westcott_2017]. Sequence error was determined using the seq.error command on mock samples after chimera removal and classification to the RDP to remove non-bacterial sequences [@mothur_schloss_2009; @vsearch_Rognes_2016; @rdp_Cole_2013].

### 2017-12-06 submission/manuscript.tex
add sequence processing methods section

@@

\hypertarget{refs}{}
\hypertarget{ref-protocol_Kozich_2013}{}
Kozich JJ., Westcott SL., Baxter NT., Highlander SK., Schloss PD. 2013.
Development of a dual-index sequencing strategy and curation pipeline
for analyzing amplicon sequence data on the MiSeq illumina sequencing
platform. \emph{Applied and Environmental Microbiology} 79:5112--5120.
DOI: \href{https://doi.org/10.1128/aem.01043-13}{10.1128/aem.01043-13}.

@@

>>>>

\textbf{\emph{Sequence Processing:}} The mothur software program was
utilized for all sequence processing steps (Schloss et al., 2009). The
protocol followed was similar to that used by Kozich, \emph{et al.}
(Kozich et al., 2013) (\url{https://www.mothur.org/wiki/MiSeq_SOP}). Two
major differences from the stated protocol were the use VSEARCH instead
of UCHIME for chimera detection and the use of the OptiClust algorithmn
instead of average neighbor for OTU generation (Edgar et al., 2011;
Rognes et al., 2016; Westcott \& Schloss, 2017). Sequence error was
determined using the seq.error command on mock samples after chimera
removal and classification to the RDP to remove non-bacterial sequences
(Schloss et al., 2009; Cole et al., 2013; Rognes et al., 2016).

@@

\hypertarget{refs}{}
\hypertarget{ref-rdp_Cole_2013}{}
Cole JR., Wang Q., Fish JA., Chai B., McGarrell DM., Sun Y., Brown CT.,
Porras-Alfaro A., Kuske CR., Tiedje JM. 2013. Ribosomal database
project: Data and tools for high throughput rRNA analysis. \emph{Nucleic
Acids Research} 42:D633--D642. DOI:
\href{https://doi.org/10.1093/nar/gkt1244}{10.1093/nar/gkt1244}.

\hypertarget{ref-uchime_Edgar_2011}{}
Edgar RC., Haas BJ., Clemente JC., Quince C., Knight R. 2011. UCHIME
improves sensitivity and speed of chimera detection.
\emph{Bioinformatics} 27:2194--2200. DOI:
\href{https://doi.org/10.1093/bioinformatics/btr381}{10.1093/bioinformatics/btr381}.

\hypertarget{ref-protocol_Kozich_2013}{}
Kozich JJ., Westcott SL., Baxter NT., Highlander SK., Schloss PD. 2013.
Development of a dual-index sequencing strategy and curation pipeline
for analyzing amplicon sequence data on the MiSeq illumina sequencing
platform. \emph{Applied and Environmental Microbiology} 79:5112--5120.
DOI: \href{https://doi.org/10.1128/aem.01043-13}{10.1128/aem.01043-13}.

\hypertarget{ref-vsearch_Rognes_2016}{}
Rognes T., Flouri T., Nichols B., Quince C., Mahé F. 2016. VSEARCH: A
versatile open source tool for metagenomics. \emph{PeerJ} 4:e2584. DOI:
\href{https://doi.org/10.7717/peerj.2584}{10.7717/peerj.2584}.

\hypertarget{ref-mothur_schloss_2009}{}
Schloss PD., Westcott SL., Ryabin T., Hall JR., Hartmann M., Hollister
EB., Lesniewski RA., Oakley BB., Parks DH., Robinson CJ., Sahl JW.,
Stres B., Thallinger GG., Horn DJV., Weber CF. 2009. Introducing mothur:
Open-source, platform-independent, community-supported software for
describing and comparing microbial communities. \emph{Applied and
Environmental Microbiology} 75:7537--7541. DOI:
\href{https://doi.org/10.1128/aem.01541-09}{10.1128/aem.01541-09}.

@@

\hypertarget{ref-opticlust_Westcott_2017}{}
Westcott SL., Schloss PD. 2017. OptiClust, an improved method for
assigning amplicon-based sequence data to operational taxonomic units.
\emph{mSphere} 2:e00073--17. DOI:
\href{https://doi.org/10.1128/mspheredirect.00073-17}{10.1128/mspheredirect.00073-17}.
